### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@f552dd62fe1d0ee94574e0ff7a95536f59860deb 🚀

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{Trivariate additive mapping of the components of risk. Viral
sharing runs from yellow (low) to blue (high); host phylogenetic
diversity runs from pink (low) to high (green) channel, and
compositional uniqueness runs from cyan (low) to red (high). The GMTC
suggests that the highest evolutionary potential for emergence exists in
unique and diverse host communities with low viral sharing, \emph{i.e.}
pixels around yellow.}\label{fig:trivariate}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:risk}{%
\centering
\includegraphics{figures/risk_map.png}
\caption{Extraction of a measure of \emph{Betacoronavirus} emergence
risk from bat hosts based on the colorimetric space from
fig.~\ref{fig:trivariate}. The risk is a composite measure of the color
value and angular distance to the yellow hue, as defined in the methods,
ranged in the unit space. Based on these analyses, South-Eastern Asia,
Madagascar, the Middle-East, and Africa below the Sahara desert have the
highest relative risk of emergence.}\label{fig:risk}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{Trivariate additive mapping of the components of risk. Viral
sharing runs from yellow (low) to blue (high); host phylogenetic
diversity runs from pink (low) to high (green) channel, and
compositional uniqueness runs from cyan (low) to red (high). The GMTC
suggests that the highest evolutionary potential for emergence exists in
unique and diverse host communities with low viral sharing, \emph{i.e.}
pixels around yellow. All components are scaled in brightness so that a
pixel with no sharing, no phylogenetic diversity, and no compositional
uniqueness would be black, and a pixel with maximal values for each
would be white.}\label{fig:trivariate}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:risk}{%
\centering
\includegraphics{figures/risk_map.png}
\caption{Evolutionary potential for zoonotic emergence of bat-origin
betacoronaviruses. Risk is a composite measure of the color value and
angular distance to the yellow hue in fig.~\ref{fig:trivariate} (see
Methods).}\label{fig:risk}
}
\end{figure}
